Towards a self healing swarm through the removal of voids and anomalies

### 2018-07-15 paper.tex
Graphic Fix

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/OilSlick}
{Concave reduction oil slick surrounding\label{voids:OilSlick}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8cm]{figures/OilSpillSimulator}
{Oil spill containment simulation\label{concave:OilSpillSimulation}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillBase1}
{Initial\label{concave:OilSpillBase1}}

%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillBase1}
%% \end{center}
%% \caption{Initial\label{concave:OilSpillBase1}}
%% \end{figure}

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillBase2}
{Partial\label{concave:OilSpillBase2}}

%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillBase2}
%% \end{center}
%% \caption{Partial\label{concave:OilSpillBase2}}
%% \end{figure}

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillBase3}
{End\label{concave:OilSpillBase3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillConcave1}
{Initial\label{concave:OilSpillConcave1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillConcave2}
{Partial\label{concave:OilSpillConcave2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillConcave3}
{End\label{concave:OilSpillConcave3}}

>>>>

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSlick}
{Concave reduction oil slick surrounding\label{voids:OilSlick}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillSimulator}
{Oil spill containment simulation\label{concave:OilSpillSimulation}}

@@

%COVERBASELINE8060OILSPILL1.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillBase1}
{Initial\label{concave:OilSpillBase1}}

%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillBase1}
%% \end{center}
%% \caption{Initial\label{concave:OilSpillBase1}}
%% \end{figure}
%COVERBASELINE8060OILSPILL3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillBase2}
{Partial\label{concave:OilSpillBase2}}

%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillBase2}
%% \end{center}
%% \caption{Partial\label{concave:OilSpillBase2}}
%% \end{figure}
%COVERBASELINE8060OILSPILL3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillBase3}
{End\label{concave:OilSpillBase3}}

@@

%COVERBASELINE8060OILSPILLCONCAVE1.py 
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillConcave1}
{Initial\label{concave:OilSpillConcave1}}

@@

%COVERBASELINE8060OILSPILLCONCAVE2.py 
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillConcave2}
{Partial\label{concave:OilSpillConcave2}}

@@

%COVERBASELINE8060OILSPILLCONCAVE3.py 
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillConcave3}
{End\label{concave:OilSpillConcave3}}
